### 2022-05-18 chapters/testing/testing.tex
draft. first chapter
Proofreading benchmarks

\newpage
\chapter{Testing}
\label{chapter:testing}

In order to optimize the energy consumption of software we first want to setup a testing enviroment. This chapter will be dedicated to provide a set of guidelines to provide a \em{reproducible, accurate} and \em{representative} tests.
Each aspect will be detailed in the sections below

\import{chapters/testing/}{reproducibility}
\import{chapters/testing/}{accuracy}
\import{chapters/testing/}{representativeness}

>>>>

\newpage

\chapter{Empirical Evaluation Protocol}
\label{chapter:testing}

To optimize the software energy consumption, a reproducible setup environment requires to be designed.
I chose to adopt an empirical approach to explore energy consumption reductions through a trial and error methodology.

%  This chapter will be dedicated to provide a set of guidelines to provide a \em{reproducible, accurate} and \em{representative} tests. Each aspect will be detailed in the sections below.

\import{chapters/testing/}{challenges}
\import{chapters/testing}{stateoftheart}
\import{chapters/testing/}{environement}
\import{chapters/testing/}{experement}
\import{chapters/testing/}{conclusion}
